API design for machine learning software: experiences from the scikit-learn project

### 2013-08-20 paper.tex
twocolumn format and decoupled from LLNCS for CiSE
Also changed some affiliations and upped the sales pitch.

\documentclass{llncs}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{minted}

@@

\pagestyle{headings}

@@

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~C.~M\"uller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{4,9} \and
        Jaques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}

\institute{ILPS, Informatics Institute, University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Independent consultant \and
           University of Bucharest \and
           Ciuvo GmbH \and
           Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

@@

\begin{abstract}
\sklearn is an increasingly popular machine learning
library. Written in Python, it is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this paper, we present and
discuss our design choices for the application programming interface (API) of
the project. In particular, we describe the simple and elegant interface shared
by all learning and processing units in the library and then discuss its
advantages in terms of composition and reusability. The paper also comments on
implementation details specific to the Python ecosystem and analyzes obstacles
faced by users and developers of the library.
\end{abstract}

\setcounter{footnote}{0}

>>>>

\documentclass[10pt,twocolumn]{article}

\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{minted}

@@

%\pagestyle{headings}

@@

\author[1]{Lars~Buitinck}
\author[2]{Gilles~Louppe}
\author[3]{Mathieu~Blondel}
\author[4]{Fabian~Pedregosa}
\author[5]{Andreas~C.~Müller}
\author[4]{Olivier~Grisel}
\author[6]{Vlad~Niculae}
\author[7]{Peter~Prettenhofer}
\author[4,8]{Alexandre~Gramfort}
\author[4]{Jaques~Grobler}
\author[9]{Robert~Layton}
\author[10]{Jake~Vanderplas}
\author[2]{Arnaud~Joly}
\author[11]{Brian Holt}
\author[4]{Gaël~Varoquaux}

\affil[1]{Netherlands eScience Center}
\affil[2]{University of Liège}
\affil[3]{Kobe University}
\affil[4]{Parietal, INRIA Saclay}
\affil[5]{University of Bonn}
\affil[6]{University of Bucharest}
\affil[7]{Ciuvo GmbH}
\affil[8]{Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI}
\affil[9]{University of Ballarat}
\affil[10]{University of Washington}
\affil[11]{Samsung Electronics Research Institute}

@@

\begin{abstract}
\sklearn is an increasingly popular machine learning library
for the Python programming language.
It is designed to be simple and efficient,
accessible to non-experts, and reusable in various contexts:
it has a user base in neuroscience, astronomy, computational linguistics,
as well as industry.

In this paper, we present and
discuss our design choices for the application programming interface (API) of
the project. In particular, we describe the simple and elegant interface shared
by all learning and processing units in the library and then discuss its
advantages in terms of composition and reusability. The paper also comments on
implementation details specific to the Python ecosystem and analyzes obstacles
faced by users and developers of the library.\footnote{
  An earlier version of this paper was presented
  at the ECML/PKDD Workshop on Languages for Data Mining and Machine Learning,
  September 2013, Prague.}
\end{abstract}

%\setcounter{footnote}{0}
